---
title: "B06705020"
output: html_notebook
---
#13.17
a.
$H_0$ : Tastee baby food isn't superior in gaining weight.
$H_1$ : Tastee baby food is superior in gaining weight.
```{r}
library("readxl")
myfile_ <- read_xlsx("Xr13-17.xlsx")
tastee <- myfile_$Tastee[!is.na(myfile_$Tastee)]
competitor <- myfile_$Competitor
var.test(x = tastee, y = competitor, alternative = "two.sided", conf.level = 0.95)
cat("According to the F test, the variances of samples are equal.")
t.test(x = tastee, y = competitor,var.equal = TRUE, alternative = "greater", conf.level = 0.95)
cat("we reject the null hypothesis and accept the alternative hypothesis, which means the Tastee is indeed superior in making babies gain weight.")
```

b.
```{r}
t.test(x = tastee, y = competitor, var.equal = TRUE, alternative = "two.sided", conf.level = 0.95)
cat("We have 95% confidence that [3.125913, 8.020754] covers the real difference of the mean weight-gain between Tastee and its competitor.")
```
c.
```{r}
hist(tastee, xlab = "Gained weight", breaks = 5)
hist(competitor, xlab = "Gained weight", breaks = 5)
```

#13.33
$H_0$ : The new steeled-belt radial tire doesn't lasts longer.
$H_1$ : The new steeled-belt radial tire lasts longer.
```{r}
myfile_ <- read_xlsx("Xr13-33.xlsx")
new <- myfile_$New
existing <- myfile_$Existing
var.test(x = new, y = existing, alternative = "two.sided", conf.level = 0.95)
cat("According to the F test, the variances of samples are equal.")
t.test(x = new, y = existing, alternative = "greater", var.equal = TRUE, conf.level = 0.95)
cat("we accept the null hypothesis, which means the new tire doesn't lasts longer.")
```

#13.37
$H_0$ : SAT score didn't increase.
$H_1$ : SAT score increases.
```{r}
myfile_ <- read_xlsx("Xr13-37.xlsx")
before <- myfile_$Before
after <- myfile_$After
var.test(x = after, y = before, alternative = "two.sided", conf.level = 0.95)
cat("According to the F test, the variances of samples are equal.")
t.test(x = after, y = before, alternative = "greater", var.equal = TRUE, conf.level = 0.95)
cat("we reject the null hypothesis and accept the alternative hypothesis, which means the SAT score increases after the change in the school's start time.")
```

#13.116
$H_0$ : The marks of the two classes have no differences.
$H_1$ : The marks if the two classes have differences.
```{r}
myfile_ <- read_xlsx("Xr13-116.xlsx")
class1 <- myfile_$`Class 1`
class2 <- myfile_$`Class 2`
var.test(x = class1, y = class2, alternative = "two.sided", conf.level = 0.95)
cat("we accept the null hypothesis, which means the marks of the two classes has no differences in variation.")
```

#13.117
$H_0$ : The speed of two weeks didn't vary.
$H_1$ : The speed of two weeks varied.
```{r}
myfile_ <- read_xlsx("Xr13-117.xlsx")
week1 <- myfile_$`Week 1`
week2 <- myfile_$`Week 2`
var.test(x = week1, y = week2, alternative = "greater", conf.level = 0.95)
cat("we reject the null hypothesis, and accept the alternative hypothesis, which means the variation of the speed of two weeks differs.")
```


