---
title: "B06705020"
output: html_notebook
---

##14.9
#a.
$H_0$ : $\mu_A$ = $\mu_B$ = $\mu_C$ = $\mu_D$

$H_1$ : Not all the means are equal.

Where $\mu_i$ is the average grade in the first year at the university of students from school i.
```{r}
library("readxl")
myfile_ <- read_xlsx("Xr14-09.xlsx")
schoolA <- myfile_$`School A`[!is.na(myfile_$`School A`)]
schoolB <- myfile_$`School B`[!is.na(myfile_$`School B`)]
schoolC <- myfile_$`School C`[!is.na(myfile_$`School C`)]
schoolD <- myfile_$`School D`[!is.na(myfile_$`School D`)]
data = data.frame(y = c(schoolA, schoolB, schoolC, schoolD), a = factor(c(rep("A", length(schoolA)), rep("B", length(schoolB)), rep("C", length(schoolC)), rep("D", length(schoolD)))))
summary(aov(y~a, data))
```
Since the p-value is 0.0437, so we reject the null hypothesis in favor of the alternative hypothesis

#b.
The population must be normally distributed.

The variances of all population tested must be equal.

The samples must be independent.

#c.
To test if all populations are normally distributed, we conduct the Shapiro-Wilk normality test.
```{r}
shapiro.test(schoolA)
shapiro.test(schoolB)
shapiro.test(schoolC)
shapiro.test(schoolD)
```
Since all p-values are greater than 0.05, we can conclude that all populations are normally distributed.

Next, to test if all of the variances are equal, we apply the Barlett's test.

$H_0$ : $\sigma_A$ = $\sigma_B$ = $\sigma_C$ = $\sigma_D$

$H_1$ : Not all of the variances are equal

Where $\sigma_i$ is the variance of grade in the first year at the university of students from school i.
```{r}
bartlett.test(y~a, data)
```
Since the p-value(0.6692) is greater than 0.05, we can conclude that all of the variances are equal.

Moreover, while the grades are individually given depending on the students' behavior, the samples should be independent.

We can conclude now the required condition of part(a) is satisfied.

##14.17
#a
$H_0$ : $\mu_1$ = $\mu_2$ = $\mu_3$

$H_1$ : Not all the means are equal.

Where $\mu_i$ is the average size of leaves from group i.
```{r}
myfile_ <- read_xlsx("Xr14-17.xlsx")
groupA <- myfile_$`Size-Group 1`
groupB <- myfile_$`Size-Group 2`
groupC <- myfile_$`Size-Group 3`
data <- data.frame(y = c(groupA, groupB, groupC), a = factor(c(rep("A", length(groupA)), rep("B", length(groupB)), rep("C", length(groupC)))))
summary(aov(y~a, data))
```
Since the p-value is 2.84e-06, we reject the null hypothesis in favor of the alternative hypothesis.

#b.
$H_0$ : $\mu_1$ = $\mu_2$ = $\mu_3$

$H_1$ : Not all the means are equal.

Where $\mu_i$ is the average amount of nicotine from group i.
```{r}
groupA <- myfile_$`Nicotine-Group 1`
groupB <- myfile_$`Nicotine-Group 2`
groupC <- myfile_$`Nicotine-Group 3`
data <- data.frame(y = c(groupA, groupB, groupC), a = factor(c(rep("A", length(groupA)), rep("B", length(groupB)), rep("C", length(groupC)))))
summary(aov(y~a, data))
```
Since the p-value is extremely small(<2e-16), we reject the null hypothesis in favor of the alternative hypothesis.

##14.21
$H_0$ : $\mu_C$ = $\mu_N$ = $\mu_T$

$H_1$ : Not all the means are equal.

Where $\mu_C$, $\mu_N$ and $\mu_T$ is the commuting time of California, New York and Texas.
```{r}
myfile_ <- read_xlsx("Xr14-21.xlsx")
California <- myfile_$California[!is.na(myfile_$California)]
NewYork <- myfile_$`New York`[!is.na(myfile_$`New York`)]
Texas <- myfile_$Texas[!is.na(myfile_$Texas)]
data <- data.frame(y = c(California, NewYork, Texas), a = factor(c(rep("Cal", length(California)), rep("New", length(NewYork)), rep("Tex", length(Texas)))))
summary(aov(y~a, data))
```
Since the p-value is 3.73e-16, we reject the null hypothesis in favor of the alternative hypothesis.
