---
title: "R Notebook"
output: html_notebook
---
#16.83
##a.
```{r}
library("readxl")
myfile_ <- read_xlsx("Xr16-07.xlsx")
price <- myfile_$Price
floor <- myfile_$Floor
model <- lm(price~floor)
data <- data.frame(floor = 20)
predict(model, data, interval = "predict", level = 0.95)
```
the selling price interval predicted with 95% confidence of a 1200 sq.ft condominium on the 20 floor is [180.004, 259.3586]

##b.
```{r}
data <- data.frame(floor = 15)
predict(model, data, interval = "confidence", level = 0.99)
```
the average selling price interval predicted with 99% confidence of a 1200 sq.ft condominium on the 15 floor is [204.8826, 219.8261]

#16.89
```{r}
myfile_ <- read_xlsx("Xr16-13.xlsx")
price <- myfile_$Price
hours <- myfile_$Hours
model <- lm(price~hours)
data <- data.frame(hours = 400)
predict(model, data, interval = "predict", level = 0.99)
```
the selling price interval predicted with 99% confidence of a 1999 24-ft. Sea Ray cruiser with 400 hours engine use is [23.32652, 34.34993]

#16.97
```{r}
myfile_ <- read_xlsx("Xr16-47.xlsx")
days <- myfile_$Days
age <- myfile_$Age
model <- lm(days~age)
data <- data.frame(age = 70)
predict(model, data, interval = "confidence", level = 0.9)
```
the interval predicted with 90% confidence of the mean number of days watching the national news on television for the population of 70-year-old is [1.891772, 2.103492]

#16.119
```{r}
myfile_ <- read_xlsx("Xr16-07.xlsx")
floor <- myfile_$Floor
price <- myfile_$Price
model <- lm(price~floor)
standarized_errors <- function(y, x) {
   n <- length(y)
   linearModelVar <- lm(y ~ x)
   a <- coef(linearModelVar)[1]
   b <- coef(linearModelVar)[2]
   se <- sigma(linearModelVar)
   x_mean <- mean(x)
   x_var <- var(x)
   h <- vector("double", length = n)
   y_p <- vector("double", length = n)
   Error <- vector("double", length = n)
   Standard_E <- vector("double", length = n)
   for(i in 1:n) {
      h[i] <- (1/n) + (x[i] - x_mean)^2 / (x_var * (n - 1))
      y_p[i] <- a + b * x[i]
      Error[i] <- y[i] - y_p[i]
      Standard_E[i] <- Error[i] / (se * sqrt(1 - h[i]))
      }
    SEh <-cbind(Standard_E,h)
}
SE <- standarized_errors(price, floor)[,1]
h <- standarized_errors(price, floor)[,2]
```
##a.
$H_0$ : the error is normally distributed.

$H_1$ : the error is not normally distributed.
```{r}
shapiro.test(SE)
```
the p-value is 0.7527, the errors are normally distributed.

##b.
$H_0$ : the errors has homoscedasticity

$H_1$ : the errors has heteroscedasticity
```{r}
a <- coef(model)[1]
b <- coef(model)[2]
Price_p <- vector("double", length = length(price))
for(i in 1:length(price)) {
   Price_p[i] <- a + b * floor[i]
   }
plot(x = Price_p, y = SE, xlab = "Predicted Price", ylab = "Standardized Error", main = "Price vs Error")
```
Do not rejected $H_0$. We can assume that the variation is constant and the mean is around 0.

##outliers and influential observations
```{r}
outliers <- abs(SE) > 2
print(outliers)
```
sample 3, 21 and 50 are outliers.
```{r}
io <- h > 6 / length(floor)
print(io)
```
there are no influential observations.

#16.125
```{r}
myfile_ <- read_xlsx("Xr16-13.xlsx")
price <- myfile_$Price
hours <- myfile_$Hours
model <- lm(price~hours)
SE <- standarized_errors(price, hours)[,1]
h <- standarized_errors(price, hours)[,2]
```

##check if error is normally distributed
$H_0$ : the error is normally distributed.

$H_1$ : the error is not normally distributed.
```{r}
shapiro.test(SE)
```
the p-value is 0.9057, so the error is normally distributed.

##check if heteroscedasticity is a problem
$H_0$ : the errors has homoscedasticity

$H_1$ : the errors has heteroscedasticity
```{r}
a <- coef(model)[1]
b <- coef(model)[2]
Price_p <- vector("double", length = length(price))
for(i in 1:length(price)) {
   Price_p[i] <- a + b * floor[i]
   }
plot(x = Price_p, y = SE, xlab = "Predicted Price", ylab = "Standardized Error", main = "Price vs Error")
```
Do not rejected $H_0$. We can assume that the variation is constant and the mean is around 0.

##check if randomness exists
$H_0$ : randomness exists

$H_1$ : randomness doesn't exist
```{r}
library("randtests")
runs.test(SE)
```
the p-value is 0.2976, so we can say the randomness exists.

##outliers and influential observations
```{r}
outliers <- abs(SE) > 2
print(outliers)
```
sample 18, 25 and 33 are outliers.
```{r}
io <- h > 6 / length(hours)
print(io)
```
the are no influential observations.

#16.137
```{r}
myfile_ <- read_xlsx("Xr16-137.xlsx")
fund <- myfile_$Fund
gold <- myfile_$Gold
model <- lm(fund~gold)
SE <- standarized_errors(fund, gold)[,1]
h <- standarized_errors(fund, gold)[,2]
```
##plot the scatter diagram
```{r}
plot(x = gold, y = fund, xlab = "Price of gold", ylab = "Value of fund", main = "Value of fund against price of gold")
abline(model)
```

##purpose a statistic model
the model is y = $\beta_0$ + $\beta_1$ * x + $\epsilon$

where y is the value of fund, x is the price of gold and $\epsilon$ is the error.

##fit the model
```{r}
print(summary(model))
```
the model is y = -20.20931 + 0.08510 * x + $\epsilon$

##residual analysis
###check outliers
```{r}
outliers <- abs(SE) > 2
print(outliers)
```
sample 8 and 28 are the outliers.

###check influential observations
```{r}
io <- h > 6 / length(gold)
print(io)
```
sample 19 is a influental observation.

###check if error is normally distributed
$H_0$ : the error is normally distributed.

$H_1$ : the error is not normally distributed.
```{r}
shapiro.test(SE)
```
the p-value is 0.08612, so the error is normally distributed.

##check if heteroscedasticity is a problem
$H_0$ : the errors has homoscedasticity

$H_1$ : the errors has heteroscedasticity
```{r}
a <- coef(model)[1]
b <- coef(model)[2]
Price_p <- vector("double", length = length(gold))
for(i in 1:length(gold)) {
   Price_p[i] <- a + b * gold[i]
   }
plot(x = Price_p, y = SE, xlab = "Predicted value of fund", ylab = "Standardized Error", main = "Value of fund vs Error")
```
Do not rejected $H_0$. We can assume that the variation is constant and the mean is around 0.

##check if randomness exists
$H_0$ : randomness exists

$H_1$ : randomness doesn't exist
```{r}
runs.test(SE)
```
the p-value is 0.4411, so the randomness exists.

##assess the fitted model
```{r}
mean(fund)
summary(model)
```
the standardized error is 0.5575, which is small compared to the mean of y (11.69714), so we can say the model fits well.

###interpretaion of R-squared
62.87% of the variation in the value of fund is explained by the variation in gold price. the rest remains unexplained by this model.

###interpretation of R
```{r}
cor(fund, gold)
```
the R value is 0.7929004, it has a very strong relationship between the value of fund and the gold price.

###t-test for the model
$H_0$ : $\beta_1$ = 0

$H_1$ : $\beta_1$ $\neq$ 0

the p-value is 4.89e-07, so we can say there is overwhelming evidence to infer that the price of gold is an important variable in the linear regression model of the value of fund.

##interpretation
the $\beta_0$ is -20.20931, but since the value of fund shouldn't be negative, this is an incorrect assessment.

the $\beta_1$ is 0.08510, means that when the price of gold goes up by 1, the value of fund goes up by 0.08510

##apply for prediction
###Predict with 95% confidence the value of fund with gold of 370 dollars.
```{r}
data <- data.frame(gold = 370)
predict(model, data, interval = "predict", level = 0.95)
```
the interval of 95% confidence the value of fund with gold of 370 dollars is [10.10353, 12.45042].

###Estimate with 95% confidence the average fund price with gold of 370 dollars.
```{r}
predict(model, data, interval = "confidence", level = 0.95)
```
the interval of 95% confidence the average fund price with gold of 370 dollars is [11.0243, 11.52964].
